Pretty darn good control: when are approximate solutions better than approximate models

### 2023-01-28 manuscript/manuscript.Rmd
added escapement vs X graphs

We used the Ray framework [@ray_package] for training, in particular we used a Ray PPOConfig object to build the algorithm using the default values for all hyper-parameters (cf. [@repo] for the code used).
The agent was trained for 250 iterations of the PPO optimization step.

@@

(py | pz) + plot_annotation(tag_levels = c('A'))
```

>>>>

We used the Ray framework [@ray_package] for training, in particular we used a Ray PPOConfig object to build the algorithm using the default values for all hyper-parameters (cf. [@repo] for the code used).
The agent was trained for 200 iterations of the PPO optimization step.

@@

escxy <- ppo_df |>
  mutate(X = X+1, Y = Y+1, Z = Z+1, escapement = (1-action)*X) |>
  ggplot(aes(X, escapement, color = Y)) +
  geom_point() +
  theme(aspect.ratio = 1/1)

escxz <- ppo_df |>
  mutate(X = X+1, Y = Y+1, Z = Z+1, escapement = (1-action)*X) |>
  ggplot(aes(X, escapement, color = Z)) +
  geom_point() +
  theme(aspect.ratio = 1/1)

((py | pz)/ (escxy | escxz)) + plot_annotation(tag_levels = c('A'))
```
